Handling Recursion in Generic Programming Using Closed Type Families

### 2018-08-22 lncs-paper.tex
Wibble

The algorithm of \K{subtermsNP} is straightforward---it traverses the product, appending current element to the result list if its type is the same as of the term \K{t}, otherwise skipping the element. We use GHC's \textsf{TypeAppications} extension to pass that type.

@@

For consumer functions, such as \K{subterms} and \K{gshow}, the type \K{X b} typically is instantiated with \K{b -> X} for some datatype \K{X}. The pattern fits equally well for defining producers, such as \K{garbitrary} from the \textsf{basic-sop} package, where \K{X b} would be instantiated with \K{Gen b}.

>>>>

The algorithm of \K{subtermsNP} is straightforward---it traverses the product, appending the current element to the result list if its type is the same as of the original term, otherwise skipping the element. We use GHC's \textsf{TypeAppications} extension to pass that type.

@@

For consumer functions, such as \K{subterms} and \K{gshow}, the type \K{X b} typically is instantiated with \K{b -> T} for some datatype \K{T}. The pattern fits equally well for defining producers, such as \K{garbitrary} from the \textsf{basic-sop} package, where \K{X b} would be instantiated with \K{Gen b}.
